\Huge{Complex State Management with Immutability}

### 2022-03-05 Paper.tex
sth

%PLEASE COPY THE FILE AND EDIT THE COPY, DO NOT EDIT THIS FILE!!!

@@

\subsection{Copy-on-Write File Systems}
% COW based file Systems
Most COW-based file systems provides the ability to take snapshots of your files.
A snapshot is a consistent image of the data at a specific point in time. By data I mean the contents of a Fle system, the contents of a database, etc. Snapshots can be read only, or read/write. Writable snapshots are also called clones. Snapshots are extremely useful and have many applications: data recovery,online data protection, undo Fle system operations, testing new installations and configurations, backup solutions, data mining, and more. 
Leveraging immutability in the implementation snapshots
% https://repositum.tuwien.at/handle/20.500.12708/10774
One of the uses of the snapshot is for enabling of consistent backups. A backup can get inconsistent if during the backup the file system is used.

@@

% \subsection{Structural Sharing}
% \subsection{Cpp example}
% $https://www.youtube.com/watch?v=y_m0ce1rzRI\&t=4081s$
% \subsection{Copy-On-Write}
% \subsection{logfilesystem}
% \subsection{Append Logs}%not important
% effecient cow reduce the overhead of threading and parallel processing
% sth
% \subsection{MVC}
% \subsection{elm}
% sth
% https://www.citationmachine.net/bibliographies/aefbbb90-00f3-449b-b369-1148cb3d2bb0
\section*{References}
[1] Berman, J. J. (2018). Immutability and Immortality. In Principles and practice of big data: Preparing, sharing, and analyzing complex information (pp. 80–85). essay, Academic Press. \newline
[2] Trcka, Nikola \& Aalst, Wil \& Sidorova, Natalia. (2009). Data-Flow Anti-patterns: Discovering Data-Flow Errors in Workflows. Proceedings of the International Conference on Advanced Information Systems Engineering (CAiSE). 5565. 425-439. 10.1007/978-3-642-02144-2_34. \newline
[3] Solarwinds: Top 4 Causes Of Storage I/O Bottlenecks \& How To Mitigate Them  \newline
[4] Norvig, P. (n.d.). Teach yourself programming in ten years. Retrieved March 5, 2022, from \url{http://norvig.com/21-days.html#answers} \newline
[5] Axelsson, L. (2017). Immutability : An Empirical Study in Scala LUDVIG AXELSSON. \newline 
[6] Smith, Jonathan \& Jr, Gerald. (1988). Effects of Copy-on-Write Memory Management on the Response Time of UNIX Fork Operations.. Computing Systems. 1. 255-278.
[7] Levrinc, R. (2008). LLFS : a copy-on-write file system for Linux [Diploma Thesis]. reposiTUm. \url{https://resolver.obvsg.at/urn:nbn:at:at-ubtuw:1-28018}

>>>>

@@

\subsection{Copy-on-Write File Systems}
% COW based file Systems pdf
COW generally follows a simple principle. As long as multiple programs need read only access to a data structure, providing them only pointers[8] which point to the same data structure, instead of copying the whole structure to a new one, is enough. If at least one of the programs needs at some point write access to the data structure, create a private copy for it. The same holds for each one of the programs which will need write access to the data structure. A new private copy will be created for them. Note that the unchanged data can still be shared between both programs. COW file systems also provides many other powerful features, But our main interest for this paper is only one of them which is snapshots.
% Most COW-based file systems provides the ability to take snapshots of your files.

A snapshot is a consistent image of the data at a specific point in time. By data I mean the contents of a Fle system, the contents of a database, etc. Snapshots can be read only, or read/write. Writable snapshots are also called clones. Snapshots are extremely useful and have many applications: data recovery, online data protection, undo Fle system operations, testing new installations and configurations, backup solutions, data mining, and more.

% Leveraging immutability in the implementation snapshots
% https://repositum.tuwien.at/handle/20.500.12708/10774
One of the uses of the snapshot is for enabling of consistent backups. A backup can get inconsistent if during the backup the file system is used. Another use of the snapshot is that the snapshot is kind of easy backup that allows for the retrieving of removed or changed data. Taking of snapshots can be set up in this way that file system could do multiple level undoes. Especially if taking of snapshots does not affect performance of the system.

% https://docs.oracle.com/cd/E19253-01/819-5461/gbcxc/index.html
When a snapshot is created, its disk space is initially shared between the snapshot and the file system, and possibly with previous snapshots. As the file system changes, disk space that was previously shared becomes unique to the snapshot, and thus is counted in the snapshot's used property. Additionally, deleting snapshots can increase the amount of disk space unique to (and thus used by) other snapshots.

A snapshot's space referenced property value is the same as the file system's was when the snapshot was created.

You can identify additional information about how the values of the used property are consumed. New read-only file system properties describe disk space usage for clones, file systems, and volumes.

@@

% \subsection{Structural Sharing}
% \subsection{Cpp example}
% $https://www.youtube.com/watch?v=y_m0ce1rzRI\&t=4081s$
% \subsection{Copy-On-Write}
% \subsection{logfilesystem}
% \subsection{Append Logs}%not important
% effecient cow reduce the overhead of threading and parallel processing
% sth
% \subsection{MVC}
% \subsection{elm}
% sth
% https://www.citationmachine.net/bibliographies/aefbbb90-00f3-449b-b369-1148cb3d2bb0
\section*{References}
[1] Berman, J. J. (2018). Immutability and Immortality. In Principles and practice of big data: Preparing, sharing, and analyzing complex information (pp. 80–85). essay, Academic Press. \newline
[2] Trcka, Nikola \& Aalst, Wil \& Sidorova, Natalia. (2009). Data-Flow Anti-patterns: Discovering Data-Flow Errors in Workflows. Proceedings of the International Conference on Advanced Information Systems Engineering (CAiSE). 5565. 425-439. 10.1007/978-3-642-02144-2_34. \newline
[3] Solarwinds: Top 4 Causes Of Storage I/O Bottlenecks \& How To Mitigate Them \newline
[4] Norvig, P. (n.d.). Teach yourself programming in ten years. Retrieved March 5, 2022, from \url{http://norvig.com/21-days.html#answers} \newline
[5] Axelsson, L. (2017). Immutability : An Empirical Study in Scala LUDVIG AXELSSON. \newline 
[6] Smith, Jonathan \& Jr, Gerald. (1988). Effects of Copy-on-Write Memory Management on the Response Time of UNIX Fork Operations.. Computing Systems. 1. 255-278.
[7] Levrinc, R. (2008). LLFS : a copy-on-write file system for Linux [Diploma Thesis]. reposiTUm. \url{https://resolver.obvsg.at/urn:nbn:at:at-ubtuw:1-28018}
[8] Kernighan, B. W., and Ritchie, D. M. The C Programming Lan-
guage, Second Edition. Prentice Hall, 1988.
